{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Wording in the basis part

	\subsection{Representing a Function in terms of a Basis} 
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Three examples of bases that are often used in practice to approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

	Both of these can be used to express or in the case of the B-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.

	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_{j}(\omega_0) \phi_j(t)
	\end{equation}

	{\color{red}We should give a reference for how to obtain these coefficients and say that for the purpose of this paper we will treat this as a black box.}

@@

	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

>>>>

	\subsection{Representing a Function in terms of a Basis} 
	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion. Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express or approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$. Then the following equation shows how a basis can be used to express a function as a weighted sum of its elements.

	\begin{equation}
		x(t) = \sum_{j \in \mathcal{I}} a_j \phi_j(t) 
	\end{equation}

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.

@@

	Its elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$. Additionally, the Fourier basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

	{\color{blue}I don't get this... Isn't the basis defined independently from the data set? Why is this dependent on the measuring points? "rephrasing \cite{ramsay_functional_2005}, the Fourier basis is orthonormal when the values $t_j$ are equally spaced within $T$."}
